DATA 621 - Business Analytics and Data Mining

### 2020-11-02 HW4/HW4_Draft.Rmd
Complete coefficient discussion.

In terms of variable importance, it can be estimated from the the last trace of
the stepping procedure shown below. The further down the table the variable is,
the more dramatic its inclusion or exclusion will be. The top 10 variables in
order would be: `URBANICITY.Urban`, `CAR_USECommercial:URBANICITYUrban`,
`REVOKED.Yes`, `TRAVTIME`, `CAR_TYPE.Sports Car`, `CLM_FREQ`, `TIF`, `MVR_PTS`,
`CAR_TYPE.SUV`, and `JOB.Blue Collar`.

@@

The interaction between `INCOME` and `HOME_VAL` serves to temper the effect of
`HOME_VAL`. Similarly for the inter

>>>>

#### Variable Importance
In terms of variable importance, it can be estimated from the the last trace of
the stepping procedure shown below. The further down the table the variable is,
the more dramatic its inclusion or exclusion will be on the deviance and theAIC.
The top 10 variables in order would be: `URBANICITY.Urban`,
`CAR_USECommercial:URBANICITYUrban`, `REVOKED.Yes`, `TRAVTIME`,
`CAR_TYPE.Sports Car`, `CLM_FREQ`, `TIF`, `MVR_PTS`, `CAR_TYPE.SUV`,
and `JOB.Blue Collar`.

@@

The interaction between `INCOME` and `HOME_VAL` serves to temper the effect of
`HOME_VAL`. Similarly for the interaction between `OLDCLAIM` and `CLM_FREQ`.

#### Variable Importance
In terms of variable importance, it can be estimated from the the last trace of
the stepping procedure shown below. There are only eight variables in the model,
and in order of AIC contribution they are `BLUEBOOK`, `OLDCLAIM`, `HOME_VAL`,
`INCOME:HOME_VAL`, `CAR_USE.Commercial`, `OLDCLAIM:CLM_FREQ`, `MSTATUS.Yes`, and
` REVOKED.Yes`.
